Effects of rotation and magnetic braking on Li abundances for solar-type stars

### 2019-06-23 project/overleaf/paper.tex
Paper v2.2
Add grid images

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_0_0g.eps}
    \label{fig:subim1}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_3_5g.eps}
    \label{fig:subim2}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_4_0g.eps}
    \label{fig:subim3}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_4_5g.eps}
    \label{fig:subim4}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_5_0g.eps}
    \label{fig:subim5}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_var_vel_5_5g.eps}
    \label{fig:subim6}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image2}
\end{figure*}
\par

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0084_var_b.eps}
    \label{fig:subim21}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_014_var_b.eps}
    \label{fig:subim22}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0196_var_b.eps}
    \label{fig:subim23}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_028_var_b.eps}
    \label{fig:subim24}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/li_vc_0336_var_b.eps}
    \label{fig:subim25}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim26}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which $v/v_{crit}$ has been fixed and the magnetic field with intensity varies between 3.5 and 5.5 G, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image22}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_0g.eps}
    \label{fig:subim41}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_3_5g.eps}
    \label{fig:subim42}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_4g.eps}
    \label{fig:subim43}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_4_5g.eps}
    \label{fig:subim44}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_5g.eps}
    \label{fig:subim45}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/rot_vel_5_5g.eps}
    \label{fig:subim46}
    \end{subfigure}
\caption{Grid showing the evolution of the evolution of surface rotational velocity, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image24}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/mb_act_3_5g.eps}
    \label{fig:subim31}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/mb_act_4_0g.eps}
    \label{fig:subim32}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/mb_act_4_5g.eps}
    \label{fig:subim33}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/mb_act_5_0g.eps}
    \label{fig:subim34}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/mb_act_5_5g.eps}
    \label{fig:subim35}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim36}
    \end{subfigure}
\caption{Grid showing the evolution of magnetic braking activation, as a function of time and the existence of a radiative core for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $v/v_{crit}$ varies between 0.0084 and 0.0336. The dashed lines make reference to the ZAMS defined as the temporal simulation instant closest to the timestep in which both the central H mass fraction has been reduced by 0.0015 from its initial value and the model first $L_H/L_{phot} \geq 0.99$, where $L_{H}$ is luminosity produced by the H burning power at the star core and $L_{phot}$ represents the star luminosity in the photosphere.}
\label{fig:image32}
\end{figure*}
